End-User Software Customization by Direct Manipulation of Tabular Data

### 2020-08-17 paper.tex
second round submission version

We developed two cell editors, to explore the benefits of adding custom
UI for editing values in the table.

One valuable feature is that users can incorporate their private
information into a web UI. We created a datepicker based on the
\href{https://fullcalendar.io/}{FullCalendar} plugin, which can load
data from a Google Calendar. This makes it convenient to enter dates
into a website based on the user's personal calendar information,
without uploading that information to the website itself.

Another benefit is that a user can choose a preferred widget for editing
information across different sites that typically provide a fragmented
editing experience. We built a text editor based on the
\href{https://ckeditor.com/}{CKEditor} rich text editor, and integrated
it with Google's Blogger website by representing the contents of a blog
post as a single table cell containing an HTML string (shown in
Figure~\ref{fig:blogger}). If there were site adapters available for
other websites with rich text entry, the user could then use a single
rich text editor to edit text across the whole web.

>>>>

We developed two \emph{cell editors}: custom UI widgets for editing
values in the table.

One benefit that cell editors provide is enabling users to incorporate
their private information into a web UI. We created a datepicker widget
(based on the \href{https://fullcalendar.io/}{FullCalendar} plugin),
which can load calendar data from a Google Calendar. This makes it
convenient to enter dates into a website based on the user's personal
calendar information, without needing to upload a user's calendar to the
website itself.

Another benefit is that a user can choose a single preferred widget for
editing a certain type of information across different sites. For
example, a user could use their favorite rich text editor to edit text
in various websites like blogging platforms and task trackers. To
demonstrate this capability, we built a text editor based on the
\href{https://ckeditor.com/}{CKEditor} rich text editor. We used the
editor with Google's Blogger website, by building a site adapter that
represented the contents of a blog post as a single table cell
containing an HTML string (shown in Figure~\ref{fig:blogger}).
